Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
symbolite and sympy

Symbolite is a lightweight symbolics package to create algebraic
mathematical expressions. Symbolite expressions can be inspected and
compiled to various backends. Currently, we have implementations for
NumPy \cite{harrisArrayProgrammingNumPy2020}; Numba \cite{lamNumbaLLVMbasedPython2015},
a \ac{JIT} compiler to LLVM; SymPy \cite{meurerSymPySymbolicComputing2017}, a
library for symbolic mathematics; and JAX \cite{jax2018github}, a
library that support automatic differentiation and compilation to \acp{GPU}
and \acp{TPU}. Symbolite is designed to facilitate the easy integration of
new backends.

>>>>

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
Unlike SymPy \cite{meurerSymPySymbolicComputing2017},
a widely-used Python library for symbolic mathematics,
it only provides the building of an expression tree
which can be inspected and compiled to various backends.
Symbolite is designed to facilitate the integration of new backends.
Currently, we have implementations for
NumPy \cite{harrisArrayProgrammingNumPy2020};
Numba \cite{lamNumbaLLVMbasedPython2015},
a \ac{JIT} compiler to LLVM;
SymPy \cite{meurerSymPySymbolicComputing2017};
and JAX \cite{jax2018github}, a
library that support automatic differentiation and compilation to \acp{GPU} and \acp{TPU}.
